---
title: "Chapter1Notes"
format:
  html:
    toc: true
editor: source
---

##General overview notes.

*Discusses basic aspects of RStudio and how to orientate one's self within the program.
  +All of this is mostly review. Nothing super revelatory here or in the workflow of R sections
  +Talks about R Script files and stuff
  
##Using R as a calculator

```{r}


#Doing simple math

1+100

72+56

5-7*2

(7-9)+23*5

((5^4)*7)/121


```

##R and Math Functions

*Talks about functions and what they are

```{r}

sin(1)

log(1)

tan(1)

log10(100) #Base ten log

exp(5) # e ^ 5

```

##Comparing values in R

*R can also compare values

```{r}
1 == 1 #looks for equality

1 != 2 #looks for inequality
1 > 10 # greater than
10 < 1 #less than

1 >= 10 #Greater than or equal to

1 <= 1 #Lesser than or equal to

5*5 == 35-10

```

##Variables and assigning them

*R allows for the creation of variables and can store them for you
  +You assign the variable to the variable itself. Cannot contain spaces or slashes
  +Several methods are used to seperate words
    - periods.between.words
    - Underscores_between_words (my_preferred_method)
    - camelCaseToSeperateWords (This one just confuses me)
  + You can also use the equal sign as an operator
  

```{r}

x <- 1/7000

x

log(x)

x <- 100

#Variable wtih itself in the assignment.

x <- x + 1

y <- x * 2
```


##Vectorization

*You can make vectors in R

```{r}

1:10

2^(1:10)

x = 1:5

2^x

```

##Managing your environment

*There are several commands that assisst with looking at and managing your environment

```{r}

ls() #Lists all of variables in environment

rm() #Removes objects adn variables

r,(list = ls()) #clears your entire environment

```

##RPackages

*Discusses R packages and a variety of commands related to them. 

##Challenges

*Challenge 1
+_age, 2widths, and min length are invalid. The rest do create variables with .mass being a hidden variable

*Challenge 2

```{r}
mass = 47.5
age = 122
mass = mass*2.8
age = age - 20
```

*Challenge 3
```{r}

mass >= age

```

*Challenge 4
```{r}

rm(age, mass)

```

*Challenge 5
```{r}

install.packages("plyr")
install.packages("gapminder")

```