---
title: "Chap4notes"
format: 
  html:
    toc: true
editor: source
---

## Data Structures

* Data in R needs to tabular (csv or excel document)
* can creat csv files from data frames you make in r
* read.table function used to read all forms of tabular data (sperated by punctuation). More broad version of read.csv
* Can pull data from frames, check factors of data, adjust the data in the data frames themselves

```{r}
dog <- data.frame(breed = c("Beagel", "Labrador", "Husky"), weight = c(15, 70, 80), plays_fetch = c(1,0,1))

#write.csv(x = dog, file = "data/canine-data.csv", row.names = FALSE), Quarto doesn't load these

#dog <- read.csv(file = "data/canine-data.csv"), Quarto doesn't load these
dog

dog$weight

dog$breed

dog$weight + 10 

paste("May dog is a", dog$breed)

```


## Data Types
Repeat of HW not writing new notes


## Vectors and Data Coercion

* Can coerce data into certain types via as.factor and other functions

```{r}
dog$plays_fetch <- as.logical(dog$plays_fetch)
```

## Matrices

* Essentially more advanced math data tables. Unlikely to be relevant for my research